---
title: "Challenge 11"
author: "Chloe Tan"
date: "2023-10-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r }
 library(httr)
 library(jsonlite)
 library(tidyverse)

```

```{r,}
historic_state_data_url <- "https://api.covidactnow.org/v2/states.timeseries.json?apiKey=19718ea06d7e476993d61dd560968285"

raw_data<-GET(historic_state_data_url)

```

```{r}
data<-fromJSON(rawToChar(raw_data$content))

```

```{r}
glimpse(data)
```

what is population in various states of USA?
```{r}
data$state
```

```{r}
data$population

```
What fraction of population was infected? 
```{r}
data$state
data$actuals$cases

```
wht fraction of recovered ppl recovered? 
```{r}
data$actuals$cases
data$actuals$deaths
data$state

```
iv)what fraction of population is currently vaccinated? 
```{r}
data$actuals$vaccinatedcompleted
data$state
```
v) what was the transmission like in various states? 
```{r}
 time_series <- data %>%
     unnest(actualsTimeseries)
```

```{r}
  time_series_transmission <- tibble(Date=time_series$cdcTransmissionLevelTimeseries[[which(data$state=="CA")]]$date)
 # Transmission levels in each state
 time_series_transmission$Alaska <- time_series$cdcTransmissionLevelTimeseries[[which(data$state=="AK")]]$
 cdcTransmissionLevel
 time_series_transmission$California <- time_series$cdcTransmissionLevelTimeseries[[which(data$state=="CA")]]$cdcTransmissionLevel
 time_series_transmission$New_Jersey <- time_series$cdcTransmissionLevelTimeseries[[which(data$state=="NJ")]]$cdcTransmissionLevel
 time_series_transmission$Tennessee <- time_series$cdcTransmissionLevelTimeseries[[which(data$state=="TN")]]$cdcTransmissionLevel
 time_series_transmission$District_of_Columbia <- time_series$cdcTransmissionLevelTimeseries[[which(data$state=="DC")]]$cdcTransmissionLevel
 
 print(head(time_series_transmission))
```
How did the disease progress since it started? 
```{r}
time_series_cases <- list(Alaska = time_series %>% filter(state=="AK") %>% select(date,cases))
 time_series_cases$California <- time_series %>% filter(state=="CA") %>% select(date,cases)
 time_series_cases$New_Jersey <- time_series %>% filter(state=="NJ") %>% select(date,cases)
 time_series_cases$Tennessee <- time_series %>% filter(state=="TN") %>% select(date,cases)
 time_series_cases$District_of_Columbia <- time_series %>% filter(state=="DC") %>% select(date,cases)
```

#Analyse the data (visualise)
#bar chart
```{r}
 ggplot(data, aes(x=state,y=population)) + geom_bar(stat="identity") +labs(x="States",y="Population") + theme_bw()
```
#scatter plots
```{r}
 ggplot(data, aes(x=state,y=(data$actuals$cases/population))) + geom_bar(stat="identity") + labs(x="State
 s",y="Infected (%)")+theme_bw()

```

```{r}
 time_series_transmission[seq(1,1300,by=100),]%>%
  pivot_longer(cols=Alaska:District_of_Columbia,names_to="Countries",values_to="Transmission") %>%
 ggplot(aes(x=Date,y=Transmission,colour=Countries,group=Countries)) +
 geom_point(show.legend=TRUE) + labs(x="Date",y="Transmission Level")+theme_bw()

```
reshape data 
```{r}
 data_to_plot <- tibble(Date_Alaska = time_series_cases$Alaska$date[seq(1,1300,by=100)],
Cases_Alaska = time_series_cases$Alaska$cases[seq(1,1300,by=100)],
Date_California =time_series_cases$California$date[seq(1,1300,by=100)],
Cases_California=time_series_cases$California$cases[seq(1,1300,by=100)],
Date_New_Jersey =time_series_cases$New_Jersey$date[seq(1,1300,by=100)],
Cases_New_Jersey=time_series_cases$New_Jersey$cases[seq(1,1300,by=100)],
Date_Tennessee =time_series_cases$Tennessee$date[seq(1,1300,by=100)],
Cases_Tennessee =time_series_cases$Tennessee$cases[seq(1,1300,by=100)],
Date_District_of_Columbia=time_series_cases$District_of_Columbia$date[seq(1,1300,by=100)],
Cases_District_of_Columbia=time_series_cases$District_of_Columbia$cases[seq(1,1300,by=100)])

 data_to_plot

```

```{r}
#install.packages("cowplot")
```

```{r}
library(cowplot)
```
#plot graphs
```{r}
fig1<- ggplot(data_to_plot, aes(x=Date_Alaska,y=Cases_Alaska)) +
 geom_point() + labs(x="Date",y="Cases", title="Alaska") + theme_bw()

 fig2<- ggplot(data_to_plot, aes(x=Date_California,y=Cases_California)) +
 geom_point() + labs(x="Date",y="Cases", title="California") + theme_bw()
 
 fig3<- ggplot(data_to_plot, aes(x=Date_New_Jersey,y=Cases_New_Jersey)) +
 geom_point() + labs(x="Date",y="Cases", title="New Jersey") + theme_bw()
 
 fig4<- ggplot(data_to_plot, aes(x=Date_Tennessee,y=Cases_Tennessee)) +
 geom_point() + labs(x="Date",y="Cases", title="Tennessee") + theme_bw()
 
 fig5<- ggplot(data_to_plot, aes(x=Date_District_of_Columbia,y=Cases_District_of_Columbia)) +
 geom_point() + labs(x="Date",y="Cases", title="District of Columbia") + theme_bw()
 
 plot_grid(fig1 + theme(legend.justification = c(0,1)),
          fig2 + theme(legend.justification = c(1,0)),
          fig3 + theme(legend.justification = c(0,1)),
          fig4 + theme(legend.justification = c(1,0)),
          fig5 + theme(legend.justification = c(0,1)),
          align = "v", axis = "lr", nrow=3,
          ncol = 2,labels = LETTERS[1:5],
          rel_heights = c(1,2))

```

```{r}

fig1<- ggplot(data_to_plot, aes(x=Date_Alaska,y=Cases_Alaska)) +
 geom_point() + labs(x="Date",y="Cases", title="Alaska") + theme_minimal()

fig2<- ggplot(data_to_plot, aes(x=Date_California,y=Cases_California)) +
 geom_point() + labs(x="Date",y="Cases", title="California") + theme_bw()
 
 fig3<- ggplot(data_to_plot, aes(x=Date_New_Jersey,y=Cases_New_Jersey)) +
 geom_point() + labs(x="Date",y="Cases", title="New Jersey") + theme_bw()
 
 fig4<- ggplot(data_to_plot, aes(x=Date_Tennessee,y=Cases_Tennessee)) +
 geom_point() + labs(x="Date",y="Cases", title="Tennessee") + theme_bw()
 
 fig5<- ggplot(data_to_plot, aes(x=Date_District_of_Columbia,y=Cases_District_of_Columbia)) +
 geom_point() + labs(x="Date",y="Cases", title="District of Columbia") + theme_bw()
 
plot_grid(fig1 + theme(legend.justification = c(0,1)), axis.text.x=element_text(size=3),
          fig2 + theme(legend.justification = c(1,0)), axis.text.x=element_text(size=3),
          fig3 + theme(legend.justification = c(0,1)), axis.text.x=element_text(size=3),
          fig4 + theme(legend.justification = c(1,0)), axis.text.x=element_text(size=3),
          fig5 + theme(legend.justification = c(0,1)), axis.text.x=element_text(size=3),
align = "v", axis = "lr", nrow=3,
          ncol = 2,labels = LETTERS[1:5],
          rel_heights = c(1,2) )

```