---
title: "Week-4: Code-along"
author: "Chloe Tan"
date: "1/9/23"
output:
  html_document:
  df_print: paged
pdf_document: default
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II. Code to edit and execute using the Code-along.Rmd file 
<br>

## A. Data Wrangling
<br>

### 1. Loading packages (Slide #16)

```{r, eval=TRUE,echo=TRUE}
# Load package tidyverse

```

### 2. Loading data-set (Slide #16)

```{r, eval=TRUE,echo=TRUE}
# Read data from the hotels.csv file and assign it to a variable named, "hotels"
hotels<-read.csv('hotels.csv')

```

### 3. List names of the variables in the data-set (Slide #19)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
names(hotels)
```


### 4. Glimpse of contents of the data-set (Slide #20)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(dplyr)
glimpse(hotels)

```
<br>

## B. Choosing rows or columns
<br>

### 5. Select a single column (Slide #24)

```{r, eval=TRUE,echo=TRUE}
# Enter code here

select(hotels,'lead_time')

```

### 6. Select multiple columns (Slide #25)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
select(hotels,'lead_time','agent','market_segment')

```

### 7. Arrange entries of a column (Slide #28)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(hotels,'hotels','lead_time')

```

### 8. Arrange entries of a column in the descending order (Slide #30)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(hotels, desc('lead_time'))

```

### 9. Select columns and arrange the entries of a column (Slide #31)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(select(hotels,'lead_time'),desc('lead_time'))

```

### 10. Select columns and arrange the entries of a column using the pipe operator (Slide #37)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels%>%select('lead_time')

```

### 11. Pick rows matching a condition (Slide #44)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%filter(children>=1)%>%select('children')

```

### 12. Pick rows matching multiple conditions (Slide #46)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
 filter(children >= 1,hotel == 'City Hotel') %>%
 select('children')

```

### 13. Non-conditional selection of rows: sequence of indices (Slide #49)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%slice(1:5)

```

### 14. Non-conditional selection of rows: non-consecutive/specific indices (Slide #50)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels%>%slice(1,3,5)

```

### 15. Pick unique rows using distinct() (Slide #52)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
 library(dplyr)
hotels %>% distinct('hotel')

```
<br>

## C. Creating new columns
<br>

### 16. Creating a single column with mutate() (Slide #56)

```{r, eval=TRUE,echo=TRUE}
# Enter code here


```

### 17. Creating multiple columns with mutate() (Slide #58)
I tried to load the library and everytime i did so, my laptop hanged so I am worried to try again. 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(dbplyr)
hotels %>%mutate(little_ones = children + babies,
 average_little_ones = mean(little_ones)) %>% select(hotel, little_ones,children,babies, average_little_ones)



```
<br>

## D. More operations with examples
<br>

### 18. count() to get frequencies (Slide #60)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels%>%count(market_segment)
```

### 19. count() to get frequencies with sorting of count (Slide #61)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
 count(market_segment, sort = TRUE)

```

### 20. count() multiple variables (Slide #62)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```

### 21. summarise() for summary statistics (Slide #63)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```

### 22. summarise() by using group_by to find mean (Slide #64)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```

### 23. summarise() by using group_by to get count (Slide #65)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```

### 24. summarise() for multiple summary statistics (Slide #67)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```

### 25. select(), slice() and arrange() (Slide #68)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```

### 26. select(), arrange() and slice() (Slide #69)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```

### 27. filter() to select rows based on conditions (Slide #73)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```

### 28. filter() to select rows based on complicated conditions (Slide #74)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```

### 29. count() and arrange() (Slide #76)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```

### 30. mutate(), select() and arrange() (Slide #77)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```


### 31. mutate(), filter() and select() (Slide #78)

```{r, eval=FALSE,echo=TRUE}
# Enter code here

```