---
title: "Challenge-6"
author: "Chloe Tan"
date: "18/9/23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Countdown Blastoff (While Loop)

Create a program that simulates a rocket launch countdown using a while loop. Start from 10 and countdown to "Blastoff!" with a one-second delay between each countdown number. Print a message when the rocket launches.

**Hint:** You may want to use `cat` command to print the countdown and `Sys.sleep` for incorporating the delay

**Output preview:** Here is how the countdown could look like 

```

```

```
```

**Solutions:**

```{r, eval=T,echo=TRUE}
# Enter code here
# Function to simulate a one-second delay
delay <- function(seconds) {
  Sys.sleep(seconds)
}

# Initialize the countdown value
countdown <- 10

# Start the countdown
while (countdown > 0) {
  cat(countdown, "...")
  countdown <- countdown - 1
  delay(1)
}

# Print the "Blastoff!" message when the countdown reaches 0
cat("Blastoff!\n")

# Print the rocket launch message
cat("Rocket has launched!\n")


```
<br>

#### Question-2: Word Reverser (for Loop)

Develop a program that takes a user-entered word and uses a while loop to print the word's characters in reverse order. For example, if the user enters "hello," the program should print "olleh."

**Hint:** You may want to use `substr` command to access each character of the input word, and `paste` command to join the reversed letters one at a time

**Solutions:** 

```{r, eval=T,echo=TRUE}
# Enter code here
# Function to reverse a string
reverse_string <- function(input_string) {
  reversed <- ""
  i <- nchar(input_string)
  while (i > 0) {
    reversed <- paste(reversed, substr(input_string, i, i), sep = "")
    i <- i - 1
  }
  return(reversed)
}

# Prompt the user for input
user_input <- readline("Enter a word: ")

# Call the reverse_string function and print the reversed word
reversed_word <- reverse_string(user_input)
cat("Reversed word:", reversed_word, "\n")



```
<br>
