---
title: "Challenge-3"
author: "Chloe Tan"
date: "28 August 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
p.comment {
background-color: #DBDBDB;
padding: 10px;
border: 1px solid black;
margin-left: 25px;
border-radius: 5px;
font-style: italic;
}

</style>

## I. Questions

#### Question 1: Emoji Expressions

Imagine you're analyzing social media posts for sentiment analysis. If you were to create a variable named "postSentiment" to store the sentiment of a post using emojis (😄 for positive, 😐 for neutral, 😢 for negative), what data type would you assign to this variable? Why? (_narrative type question, no code required_)

**Solution:**  I would assign it as a character data type. These emojis have a string of alphabets to label the 3 different catergories. In addition, the data type would also be ordinal because there is a natural ordering from positive to neutral to negative. This shows the range of emotions respondents can reply with ranging from a positive to non-positive response. Therefore, the data type is an ordinal character data type.


#### Question 2: Hashtag Havoc

In a study on trending hashtags, you want to store the list of hashtags associated with a post. What data type would you choose for the variable "postHashtags"? How might this data type help you analyze and categorize the hashtags later? (_narrative type question, no code required_)

**Solution:** The data type for hashtags is a nominal data type. This is because they did not specify the hashtags if there is a specific natural ordering. In addition, they are catergorical data types because the hashtags may be a character since hashtags may consist of a string of alphabets or a single letter to label a hastag to a post. Therefore, this is a nominal character data type.


#### Question 3: Time Traveler's Log
  
You're examining the timing of user interactions on a website. Would you use a numeric or non-numeric data type to represent the timestamp of each interaction? Explain your choice (_narrative type question, no code required_)

**Solution:** To represent the time stamp of each user interaction, I would use a numeric data type because they can log the integer time which is a finite and discrete number eg 20 00. Numeric numbers are also double variables  so they can log the minute hand of the user interaction. The minute hand would appear as a "decimal" when we look at the time through an hour clock, so we may get the precise time through using a numeric data type.


#### Question 4: Event Elegance

You're managing an event database that includes the date and time of each session. What data type(s) would you use to represent the session date and time? (_narrative type question, no code required_)

**Solution:**  To represent session date I would use a an ordinal catergorical data. This is because dates have a natural ordering so you can classify the date according to the duration from the  start to end of the event. To classify the event time, I would use a numeric continuous variable. This is because, the hour hand may be recorded as an integer while the minute hand can be recorded like a 'decimal' when we look at time through the hour clock. 

#### Question 5: Nominee Nominations
You're analyzing nominations for an online award. Each participant can nominate multiple candidates. What data type would be suitable for storing the list of nominated candidates for each participant?  (_narrative type question, no code required_)

**Solution:** nominal catergorical data type.

#### Question 6: Communication Channels
In a survey about preferred communication channels, respondents choose from options like "email," "phone," or "social media." What data type would you assign to the variable "preferredChannel"? (_narrative type question, no code required_)

**Solution:**  I would assign a nominal categorical data. The replies are not of a natural ordering and they are a character type since the replies eg 'email', is a string of alphabets. 

#### Question 7: Colorful Commentary

In a design feedback survey, participants are asked to describe their feelings about a website using color names (e.g., "warm red," "cool blue"). What data type would you choose for the variable "feedbackColor"? (_narrative type question, no code required_)

**Solution:** I would choose a nominal categorical data type because colours do not hav a natural ordering. They are character type because they are words to represent an object and can be catergorized as different responses.  

#### Question 8: Variable Exploration

Imagine you're conducting a study on social media usage. Identify three variables related to this study, and specify their data types in R. Classify each variable as either numeric or non-numeric.

**Solution:** 
1. total usage timing : numeric and double
2. user traffic: numeric, integer
3. rating how much the like the social media platform they are using ( very pleasant, plesant, neutral, unpleasant ): non-numeric and character. 


#### Question 9: Vector Variety

Create a numeric vector named "ages" containing the ages of five people: 25, 30, 22, 28, and 33. Print the vector.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
ages<-seq(from=22,to=33,by=3)
print(ages)
```

#### Question 10: List Logic

Construct a list named "student_info" that contains the following elements:

  - A character vector of student names: "Alice," "Bob," "Catherine"

  - A numeric vector of their respective scores: 85, 92, 78

  - A logical vector indicating if they passed the exam: TRUE, TRUE, FALSE

Print the list.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
x<-('student_info')
typeof(x)
student_names<-c('Alice','Bob','Catherine')
typeof(student_names)
scores<-c(85,92,78)
typeof(scores)
passed<-c(TRUE,TRUE,FALSE)
typeof(passed)

student_info=list(student_names,scores,passed)
print(student_info)


```

#### Question 11: Type Tracking

You have a vector "data" containing the values 10, 15.5, "20", and TRUE. Determine the data types of each element using the typeof() function.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
x<-('data')
x<-c(10,15.5,"20",TRUE)
typeof(x)
```

#### Question 12: Coercion Chronicles

You have a numeric vector "prices" with values 20.5, 15, and "25". Use explicit coercion to convert the last element to a numeric data type. Print the updated vector.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
x<-('Prices')
x<-c(20.5,15,"25")
x<-as.numeric(x)
typeof(x)
print(x)
```

#### Question 13: Implicit Intuition

Combine the numeric vector c(5, 10, 15) with the character vector c("apple", "banana", "cherry"). What happens to the data types of the combined vector? Explain the concept of implicit coercion.

**Solution:** The data is combined into 1 string of numbers and characters. Implicit coercion is combining 2 seperate vectors into 1 vector and the new vector becomes a 'character' type vector because the new vector has both numerical numbers and a string of alphabets to make a word. 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
x<-c(5,10,15)
y<-c('apple','banana','cherry')
z<-cbind(5,10,15,'apple','banana','cherry')
print(z)
typeof(z)


```

#### Question 14: Coercion Challenges

You have a vector "numbers" with values 7, 12.5, and "15.7". Calculate the sum of these numbers. Will R automatically handle the data type conversion? If not, how would you handle it?

**Solution:** NO, r does not automitically handle the data type conversion. 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
x<-c('numbers')
Numbers<-c(7,12.5, "15.7")
Numbers<-as.numeric(Numbers)
print(Numbers)
sum(Numbers)


```

#### Question 15: Coercion Consequences

Suppose you want to calculate the average of a vector "grades" with values 85, 90.5, and "75.2". If you directly calculate the mean using the mean() function, what result do you expect? How might you ensure accurate calculation?

**Solution:** we get argument is not numeric or logical. 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
grades<-c(85,90.5,"75.2")
print(grades)
grades<-as.numeric(grades)
mean(grades)

```

#### Question 16: Data Diversity in Lists

Create a list named "mixed_data" with the following components:

  - A numeric vector: 10, 20, 30
  
  - A character vector: "red", "green", "blue"

  - A logical vector: TRUE, FALSE, TRUE
  
Calculate the mean of the numeric vector within the list.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
mixed_data<-list(c(10,20,30),c('red','green','blue'),c(TRUE,FALSE,TRUE))
print(mixed_data)

```

#### Question 17: List Logic Follow-up

Using the "student_info" list from Question 10, extract and print the score of the student named "Bob."

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
print(student_info)
names(student_info)<-c('student_names','scores','passed')
student_info$scores[2]


```

#### Question 18: Dynamic Access

Create a numeric vector values with random values. Write R code to dynamically access and print the last element of the vector, regardless of its length.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
dynamic_vector<-c(2,4,6,8,10,12)
print(dynamic_vector)
tail(dynamic_vector,'1')
dynamic_vector2<-c(10,20,30,40000,25)
print(dynamic_vector2)
tail(dynamic_vector2)
```

#### Question 19: Multiple Matches

You have a character vector words <- c("apple", "banana", "cherry", "apple"). Write R code to find and print the indices of all occurrences of the word "apple."

**Solution:** 

```{r, eval=FALSE,echo=TRUE}
# Enter code here
character_vector<-c('apple','banana','cherry','apple')
print(character_vector)
sum(character_vector=='apple')
```

#### Question 20: Conditional Capture

Assume you have a vector ages containing the ages of individuals. Write R code to extract and print the ages of individuals who are older than 30.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here

ages<-c(10,20,25,35,40,55,60,70)
print(ages)
ages[ages>30]





```

#### Question 21: Extract Every Nth

Given a numeric vector sequence <- 1:20, write R code to extract and print every third element of the vector.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
Vector3<-1:20
print(x)
ThirdElement <- Vector3[seq(3L,length(Vector3),3)]
print(ThirdElement)
```


#### Question 22: Range Retrieval

Create a numeric vector numbers with values from 1 to 10. Write R code to extract and print the values between the fourth and eighth elements.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
Vector4 <- 1:10
print(Vector4)
Vector4[4:8]

```

#### Question 23: Missing Matters

Suppose you have a numeric vector data <- c(10, NA, 15, 20). Write R code to check if the second element of the vector is missing (NA).

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
Vector5 <- c(10,NA,15,20)
print(Vector5)
which(is.na(Vector5))
```

#### Question 24: Temperature Extremes

Assume you have a numeric vector temperatures with daily temperatures. Create a logical vector hot_days that flags days with temperatures above 90 degrees Fahrenheit. Print the total number of hot days.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hot_days <- c(87,91,35,100,150,170,180,92,95,75)
typeof(hot_days)
hot_days_logical <- hot_days>90
print(hot_days_logical)
sum(hot_days_logical)
```

#### Question 25: String Selection

Given a character vector fruits containing fruit names, create a logical vector long_names that identifies fruits with names longer than 6 characters. Print the long fruit names.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
fruits <- c("pineapple", "strawberry", "banana", "kiwis", "apple", "pear", "orange")
#print(fruits)
long_names <- nchar(fruits)>6
print(fruits[long_names])
```

#### Question 26: Data Divisibility

Given a numeric vector numbers, create a logical vector divisible_by_5 to indicate numbers that are divisible by 5. Print the numbers that satisfy this condition.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
Numbers <- 1:50
divisible_by_5 <- Numbers[seq(5L,length(Numbers),5)]
print(divisible_by_5)

```

#### Question 27: Bigger or Smaller?

You have two numeric vectors vector1 and vector2. Create a logical vector comparison to indicate whether each element in vector1 is greater than the corresponding element in vector2. Print the comparison results.

**Solution:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
vector1 <- c(1,2,3,6,8,10,13,71)
vector2 <- c(1,5,3,8,10,17,21,34)
comparison <- vector1>vector2
print(comparison)
```

