---
title: "Week 13 Final Submision"
author: "Chloe Tan"
date: "2023-11-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Week 9 (I am changing my topic question! )

Q1) The topic finalized is friendship line phone calls amongst older adults in California during Covid 19.

Q2) The data sources I have found are friendship-line-california-calls-in-response-to-covid-19 and friendship-line-services-provided-to-older-adults-in-response-to-covid-19 (during the year 2020) . 


Week 10

Qn 1) Are Friendship-line Calls relevant in California? 

Qn2) Why is it important? 

1) According to Cherry, which was medically revised by Gans, social isolation ( which was the impact of Covid-19 and isolation measures), social isolation can lead to medical conditions like weakened immunity and high blood pressure etc. Therefore, social isolation can reduce people's bodily health which will impact their ability to live longer. Hence, friendship-lines may help make people feel less lonely because they have someone to talk to and share their worries or to hear nice encouragement. 

2) Social isolation may lead to potential mental hazards according to Tulane University. For example, "loneliness was associated with 40% increase in the rick of dementia". Therefore, Covid-19 had forced many to be in isolation and experience loneliness. consequently, Covid-19 may cause people to feel loneliness. Hence, friendship-lines may help make people feel less lonely because they have someone to talk to and share their worries or to hear nice encouragement. 

3) This can help to encourage older people to utilize friendship lines. Since, we often focus on mental health of teenagers and youths, I think its important to show that older adults can and should use friendship lines if they face loneliness or social isolation. 

Qn 3) 
Rows: County ( different parts of California), Months(from April 2020 to June 2020)

Columns: the Different counties with the highest response of older adults using the friendship line

Week 11: 

Qn1) 
Scatter plot : 

I will plot the variables Number of friendship calls in California (y axis) against the date of the friendship call (x axis)

bar charts: 

I will consolidate the number of friendship calls in a month eg 04_2020 for the various counties in California

Qn2) 
I plan to make the story interactive by making my bar charts interactive with plotly because it has ggplotly which makes ggplots interactive. 

eg the packages needed : plotly, ggplot2,dplyr,car,babynames,gapminder

graph<-ggplot(data=iris,aes(month,Number of friendship calls))+geom_point(aes(colour=County))+ggtitle(Number of friendship calls in California)

ggplotly(name of graph) # the command to make graph interactive

link:

https://www.geeksforgeeks.org/create-interactive-ggplot2-graphs-with-plotly-in-r/ 

EDIT: 
I have experienced challenges in finding ways to showcase my data. As my dataset has 60 counties and only shows the number of friendship calls, my previous method of a scatterplot was not the best way to showcase the data. 
However, through Shiny my Prof helped guide me to use create an app that shows the individual line plot graphs of each County. Therefore, people can easily see how many frienship calls were made per county. This was a better way to translate the data i have into a "story". 

```{r}

#Qn3) 
#Concepts taught vs self learned: 

concepts<-data.frame(Concepts_taught=c("drawing graphs" ,"reshape or picking up  data","insert photos"),weeks=c("7","4","1"),Self_learned=c("nil","nil","nil")
                     )

print(concepts)

```

Week 12
I experienced challenges such as not being able to upload my 2 apps. I tried many ways to solve the issue, even looking at the app hosted on my local computer to solve the problem. In the end, with the help of the TA's I found that the issue was due to the app not having the Tidy_Calls_Monthly dataset. In addition, after adding the data set inside, I had to make adjustments to my code because the shiny app did not recognize the column headings with spaces in between. Therefore to remedy the situation, I had to replace the heading "Number of calls" to "Number.of.calls". It was difficult because it took me a while to figure out the problem. However, I am glad I did. 

In addition, I found out my original plan to make a scatter plot was not the best way to display my data set. Therefore, I had to find new ways to display the data set. While prof guided me with one example, I had to get creative in using the numbers to draw an inference from to help guide my story. In the end, I decided to create a tab set data set which summarized and calculated the number of calls, the top 15% and bottom 15% of Counties with the most and least number of calls respectively. I used this to draw out the inequalities between the Counties in terms of how much Friendship-line services were utilized in the respective Counties based on the number of calls made. 


Week 13, FINAL SUBMISSION (500 words minimum, 1.2 Maximum)

(1) What is the theme of your data story?

The Theme is "Its okay not to be okay".

(2) Why is it important to address this question?

Often, we overlook the importance a phone call can have on someone. During the Covid-19 Pandemic, many were forced into isolation away from our friends, family and the people we love. This took a toll on many who experiences feelings of loneliness and social isolation. Therefore, a phone call would be extremely helpful to cheer someone up because they would feel less lonely. As shown by Cherry, social isolation can lead to medical conditions like weakened immunity and high blood pressure etc.Therefore, a friendship call would allow individuals someone to talk to and they would feel less lonely. This may help reduce the likelihood of a weakened immunity. Not only would social isolation lead to a weakened immunity, but Social isolation may lead to potential mental hazards like dementia according to Tulane University. Therefore, friendship calls may be a solution to help people feel less lonely. I believe that friendship calls should be utilized even if we are not experiencing quarantine but can be used during our day to day lives if ever we feel lonely. It is important to address the feelings of loneliness and social isolation through showing a "way" to feel less lonely. This "way" is through a friendship call.


(3) Why do you think the data sources that you have curated can help you answer the question?

My question is "Are Friendship-line Services relevant in California?" ( changes "calls" in Week 9 to "services"  )

I think the data sources have helped answer my question because they show how friendship calls are utilized in California based on the individual counties. The data sources show how many friendship calls were made during April 2020 to July 2020 ( these months are during the Covid-19 Pandemic where many were away and thus isolated from people ). 

Therefore, the data sources can tell us friendship calls were a useful way for people to feel less lonely which helps combat problems like weakened immunity and mental health issues. This highlights the relevance of Friendship calls to improve the lives of the Californian people. 


(4) What are the insights from the data and how are they depicted in plots?

The raw data shows the total number of Friendship calls in a day from April 2020 to July 2020 by County. 

1) I tidied the data and combined the days into months so that we can see how different counties have different number of calls made. They are depicted through the summary table that organised the data sources by County and by Month, ( we shall call the table Plot 1).Therefore, someone can extract the raw numbers easily if they want an exact number of the Friendship calls in a particular county. However, I used month instead of day because not many analysis would compare phone calls made in a day because the number is too specific and does not contribute to useful qualitative analysis. 

2) I made plot 2 (with the help of Prof) that tracks the monthly progression or regression of calls by county. This allows people to see how the number of Friendship calls needed in that particular county is like. This makes it easier for people to visualize the number of calls because California has too many counties (60) that can be charted in one interactive plot. Plot 2 is concerned with seeing how well the friendship call services did during April to July 2020 based on the number of calls made to the Friendship call Service.

3) I summarized the most, least, average and medium number of friendship calls for each county so its easier to extrapolate the numbers compared to extrapolating from a Plot 2. I also looked at the top 10 and bottom 10 countries so we can see the disparities between the number of Friendship calls used in the top 15% and bottom 15% of the counties in California. I chose 15% because I think it is a representative sample to cover the extreme top and bottom counties that utilized the Friendship calls so that I can make comparisons to see if Friendship calls are relevant to the people of California.  


(5) How did you implement this entire project? Were there any new concepts that you learnt to implement some aspects of it?

I implemented this project on a qmd page titled "Project.qmd" so that my website would be organised based on my introduction,the purpose of this website (about page) and one example of a data story (Project.qmd).

I started with Tidying up the raw data set to create a table which showed a brief overview of the number of Friendship calls by county. After which I created a shiny app to integrate into my website. Instead of using a template example which shiny provided, I learnt how to create an app from scratch which shows the bottom 10 and top 10 counties with the number of their friendship calls respectively. This was partly new to me because we did not go into detail during week 8 lecture on how to create a shiny app from scratch. While we were given the 3 main items (UI, server and run the app commands), it was especially challenging trying to figure out the in between which was curating the table to show the tab-sets I want and what statistics I want to get from my data set into the summary table. I think this helped to add onto my existing knowledge of shiny apps and how to create a personalized app without relying on the given examples. 

In the process of creating interactive plots, I had learned how to use Plotly, which is an app that creates interactive scatter plots, bar charts. Even though, I later found out it does not best represents my data set I think Plotly is still useful for my learning. In the future, when I find a data set that can be represented with a scatter plot, I may use plotly for Scatter, Bar, Area charts etc.  



#References 

California Population 2023 (Demographics, maps, graphs). (n.d.). Retrieved 23 November 2023, from https://worldpopulationreview.com/states/california-population

Friendship line services provided to older adults in r... 19—Dataset by chhs. (n.d.). Data.World. Retrieved 22 November 2023, from https://data.world/chhs/d71df234-7ba1-42e7-98bc-160a55beb7d1

How to embed a shiny app on website – data science genie. (n.d.). Retrieved 22 November 2023, from https://datasciencegenie.com/how-to-embed-a-shiny-app-on-website/

Park, S., & Jung, D. (Directors). (2020, June). Its Okay to Not Be Okay.

The impact of social isolation on mental health. (n.d.). Verywell Mind. Retrieved 22 November 2023, from https://www.verywellmind.com/the-impact-of-social-isolation-on-mental-health-7185458

Understanding the effects of social isolation on mental health. (2020, December 8). https://publichealth.tulane.edu/blog/effects-of-social-isolation-on-mental-health/

#Word count: 1,094 words (excluding questions and Title headers)


#QMD Files for Website is inside the Week 13 Folder. 
# Thank you for your patience in teaching me Prof :).








