---
title: "Challenge-5"
author: "Chloe Tan"
date: "11/9/23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Local Variable Shadowing 

Create an R function that defines a global variable called `x` with a value of 5. Inside the function, declare a local variable also named `x` with a value of 10. Print the value of `x` both inside and outside the function to demonstrate shadowing.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
x<-5
five<-function(){x<-10}
print(five())
print(x)
```
<br>

#### Question-2: Modify Global Variable

Create an R function that takes an argument and adds it to a global variable called `total`. Call the function multiple times with different arguments to accumulate the values in `total`.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
total<-3
multiple_totals<-function(value){total<<-total+value}
multiple_totals(7)
multiple_totals(8)
print(total)


```
<br>

#### Question-3: Global and Local Interaction 

Write an R program that includes a global variable `total` with an initial value of 100. Create a function that takes an argument, adds it to `total`, and returns the updated `total`. Demonstrate how this function interacts with the global variable.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
total<-100

additional<-function(value){total<<-total+value}
additional(5)
print(total)

```
<br>

#### Question-4: Nested Functions

Define a function `outer_function` that declares a local variable `x` with a value of 5. Inside `outer_function`, define another function `inner_function` that prints the value of `x`. Call both functions to show how the inner function accesses the variable from the outer function's scope.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
outer_function<-function(x=5){inner_function=x}
print(outer_function())
```
<br>

#### Question-5: Meme Generator Function

Create a function that takes a text input and generates a humorous meme with the text overlaid on an image of your choice. You can use the `magick` package for image manipulation. You can find more details about the commands offered by the package, with some examples of annotating images here: https://cran.r-project.org/web/packages/magick/vignettes/intro.html

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(magick)

generate_meme<-function(text,filename){
  font_size<-30
  font_colour<-'blue'
  font_size<-'Arial'
  base_image<-image_read(filename)
  base_image<-image_annotate(base_image,text,size=50, gravity = "south")
  image_write(base_image, path = "output.jpg")
}


generate_meme("a", "meme.jpg")
  
```
<br>

#### Question-6: Text Analysis Game  

Develop a text analysis game in which the user inputs a sentence, and the R function provides statistics like the number of words, characters, and average word length. Reward the user with a "communication skill level" based on their input.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
game<-function(){cat('welcome to game!\n')}
user_input<-readline(prompt='enter sentence')
words<- unlist(strsplit(user_input, split=''))
number_of_words<-length(words)
number_of_characters<-sum(nchar(words))
average_word_length<-mean(nchar(words))
skill_level<-ifelse(average_word_length>=10,'good', ifelse(average_word_length<=10,'improving'))

print(paste0('results:'))
print(paste0('number of words:',number_of_words))
print(paste0('number of characters:',number_of_characters))
print(paste0('average word length:', average_word_length))
print(paste0('communication skill level', skill_level))

game()


```
<br>